The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-04-27 VegOzone.tex
Corection of wording.

The locations of the atmospheric monitoring site as well as the ozone garden with respect to the main buildings of the Svanhovd Environment Centre are marked in the aerial photography shown in Fig.~\ref{fig:svanhovd_research_station}. The Centre is located south of the settlement of Svanvik, where as the border to Russia, the Pasvik river, lies only a few hundred meters to the east. The original farm buildings, protected by law, are located in the lower center, while the Svanhovd Environment Centre follows to the north-east. The Centre hosts offices, a conference center, a national park center, a brown bear exhibition as well as a modern laboratory for DNA analysis. Left of the Centre and north of the original farm buildings a botanical garden can be found. It is one amongst three such gardens north of the Polar Circle. The Svanhovd Environment Centre focuses on research of the special environment of the region, but also comprises long-term observations of various agrameteorological variables, i.a. $2\,\unit{m}$ temperature, precipitation, global irradiance, and soil temperature at different depths.

@@

All agrameteorological variables including temperature and precipitation are available from September 1992 to present day (LandbruksMeteorologisk Tjeneste provided by NIBIO -- \href{https://lmt.nibio.no/}{lmt.nibio.no}, note the station name here is Pasvik).

>>>>

The locations of the atmospheric monitoring site as well as the ozone garden with respect to the main buildings of the Svanhovd Environment Centre are marked in the aerial photography shown in Fig.~\ref{fig:svanhovd_research_station}. The Centre is located south of the settlement of Svanvik, where as the border to Russia, the Pasvik river, lies only a few hundred meters to the east. The original farm buildings, protected by law, are located in the lower center, while the Svanhovd Environment Centre follows to the north-east. The Centre hosts offices, a conference center, a national park center, and a modern laboratory for DNA analysis. Left of the Centre and north of the original farm buildings a botanical garden can be found. It is one amongst three such gardens north of the Polar Circle. The Svanhovd Environment Centre focuses on research of the special environment of the region, but also comprises long-term observations of various agrometeorological variables, i.a. $2\,\unit{m}$ temperature, precipitation, global irradiance, and soil temperature at different depths.

@@

All agrometeorological variables including temperature and precipitation are available from September 1992 to present day (LandbruksMeteorologisk Tjeneste provided by NIBIO -- \href{https://lmt.nibio.no/}{lmt.nibio.no}, note the station name here is Pasvik).
